\caption{Data Driven Simulation Scenario \# 1: Factorization in Equation~\eqref{eqn:levis_factorization}, 1 partially missing confounder.}
\caption{Data Driven Simulation Scenario \# 2: Factorization in Equation~\eqref{eqn:levis_factorization}, 1 partially missing confounder, additional non-linearities and interactions in imputation mean model,induced skew in distribution of imputation model.}
\caption{Data Driven Simulation Scenario $\# 3$: Factorization in Equation~\eqref{eqn:levis_factorization}, 2 partially missing confounders, amplified interactions between $A, L_{p}$, and $Y$ in joint imputation model, induced skew in distribution of imputation model.}
\caption{Data Driven Simulation Scenario \#4: Alternative factorization, 2 partially missing confounders, amplified interactions between $L_{c}, L_{p}$ in full treatment model $\tilde{\eta}
\caption{Data Driven Simulation Scenario \#5: Replication of simulation from Levis \etal\cite{levis2022} paper: Factorization in Equation (1), 1 partially missing confounder.}
\caption{Data Driven Simulation Scenario \#6: Factorization in Equation (1), 1 partially missing confounder, dampen some of the effects amplified in treatment model and imputation model in scenario \#5 to correct near-positivity violations.}
\caption{Data Driven Simulation Scenario \#7: Factorization in Equation (1), 1 partially missing confounder, amplify interactions in treatment model.}
\caption{Data Driven Simulation Scenario \#8: Factorization in Equation (1), 1 partially missing confounder, introduce non-linearities in imputation model.}
\caption{Data Driven Simulation Scenario \#9: Factorization in Equation (1), 2 partially missing confounders, extend scenario \#6 to have a second partially missing confounder.}
\caption{Data Driven Simulation Scenario \#10: Factorization in Equation (1), 2 partially missing confounders, extend scenario \#7 to have a second partially missing confounder.}
\caption{Data Driven Simulation Scenario \#11: Factorization in Equation (1), 2 partially missing confounders, extend scenario \#1 to have a second partially missing confounder (baseline simulation in main paper with a second missing confounder).}
\caption{Data Driven Simulation Scenario \#12: Factorization in Equation (1), 2 partially missing confounder, extend scenario \#8 to have a second partially missing confounder.}
\caption{Data Driven Simulation Scenario \#13: Factorization in Equation (1), 2 partially missing confounder, extend scenario \#2 to have a second partially missing confounder.}
\caption{Data Driven Simulation Scenario \#14: Factorization in Equation (1), 2 partially missing confounders, additional non-linearities and interactions in imputation model for first missing confounder, induce skew in imputation model for first missing confounder, imputation model for second missing confounder depends only on $L_{p1}$ with amplified relationship to emphasize importance of modeling $\lambda_1(\ell_{p1} ~|~ L_c, A, Y, S = 1)$ correctly.}
\caption{Data Driven Simulation Scenario \#15: Factorization in Equation (1), 2 partially missing confounders, extend scenario \#14 such that imputation model for second missing confounder depends only on both $L_{p1}$ and $Y$.}
\caption{Data Driven Simulation Scenario \#16: Factorization in Equation (1),, 2 partially missing confounders amplify effect of outcome $Y$ in imputation model for second missing confounder.}
\caption{Data Driven Simulation Scenario \#17: Factorization in Equation (1), 2 partially missing confounders, introduce interaction between treatment $A$ and outcome $Y$ in imputation model for second missing confounde.}
\caption{Data Driven Simulation Scenario \#18: Alternative factorization, 1 partially missing confounder.}
\caption{Data Driven Simulation Scenario \#19: Alternative factorization, 1 partially missing confounder, introduce interactions between $L_c$ and $L_p$ in treatment model $\tilde\eta(L_c, L_p a)$.}